Finding Code Clone Refactoring Techniques by Mapping Clone Context

### 2021-11-20 cefp/paper.tex
Updates from Overleaf

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage{float}
\usepackage{hyperref}
\usepackage[style=ieee,citestyle=numeric-comp,dashed=false]{biblatex}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{todonotes}
\addbibresource{refs.bib}
\usepackage{makecell}

@@

\begin{table}[H]
\centering
\begin{tabular}{@{}l|l|rr|rr@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{Relation}} & \textit{\textbf{Clone Classes}} & \textit{\textbf{\%}} & \textit{\textbf{Total}} & \textit{\textbf{\%}} \\ \midrule
\multirow{2}{*}{Common Class} & Same Class & 22,893 & 26.8\% & \multirow{2}{*}{31,848} & \multirow{2}{*}{37.2\%} \\ \cmidrule(lr){2-4}
 & Same Method & 8,955 & 10.5\% & & \\ \midrule
\multirow{5}{*}{Common Hierarchy} & Sibling & 15,588 & 18.2\% & \multirow{5}{*}{20,342}& \multirow{5}{*}{23.8\%} \\ \cmidrule(lr){2-4}
 & Superclass & 2,616 & 3.1\% & & \\ \cmidrule(lr){2-4}
 & First Cousin & 1,219 & 1.4\% & & \\ \cmidrule(lr){2-4}
 & Common Hierarchy & 720 & 0.8\% & & \\ \cmidrule(lr){2-4}
 & Ancestor & 199 & 0.2\% & & \\ \midrule
\multirow{4}{*}{Unrelated} & No Direct Superclass & 10,677 & 12.5\% & \multirow{4}{*}{20,314}& \multirow{4}{*}{23.7\%} \\ \cmidrule(lr){2-4}
 & External Superclass & 4,525 & 5.3\% & & \\ \cmidrule(lr){2-4}
 & External Ancestor & 3,347 & 3.9\% & & \\ \cmidrule(lr){2-4}
 & No Indirect Superclass & 1,765 & 2.1\% & & \\ \midrule
\multirow{2}{*}{Common Interface} & Same Direct Interface & 7,522 & 8.8\% & \multirow{2}{*}{13,074} & \multirow{2}{*}{15.3\%} \\ \cmidrule(lr){2-4}
 & Same Indirect Interface & 5,552 & 6.5\% & & \\ \bottomrule
\end{tabular}
\caption{Number of clone classes per clone relation.}
\label{tab:relation}
\end{table}

@@

\begin{table}[H]
\centering
\begin{tabular}{@{}lrr@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{Clone instances}} & \textit{\textbf{\%}} \\ \midrule
Method Level & 232,545 & 78.43\% \\
Class Level & 50,402 & 17.00\% \\
Constructor Level & 10,039 & 3.39\% \\
Interface Level & 2,693 & 0.91\% \\
Enum Level & 788 & 0.27\% \\
\end{tabular}
\caption{Amount of clone instances with a per location category.}
\label{tab:location}
\end{table}

@@

\begin{table}[H]
\centering
\begin{tabular}{@{}l|l|rr|rr@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{Contents}} & \textit{\textbf{Clone instances}} & \textit{\textbf{\%}} & \textit{\textbf{Total}} & \textit{\textbf{\%}} \\ \midrule
\multirow{2}{*}{Partial} & Method Body & 219,540 & 74.05\% & \multirow{2}{*}{229,521}& \multirow{2}{*}{77.42\%} \\ \cmidrule(lr){2-4}
 & Constructor Body & 9,981 & 3.37\% & & \\ \midrule
\multirow{3}{*}{Other} & Several Methods & 22,749 & 7.67\% & \multirow{3}{*}{53,773} & \multirow{3}{*}{18.14\%} \\ \cmidrule(lr){2-4}
 & Only Fields & 17,700 & 5.97\% & & \\ \cmidrule(lr){2-4}
 & Other & 13,324 & 4.49\% & & \\ \midrule
 \multirow{5}{*}{Full} & Full Method & 12,990 & 4.38\% & \multirow{5}{*}{13,173}& \multirow{5}{*}{4,44\%} \\ \cmidrule(lr){2-4}
  & Full Interface & 64 & 0.02\% & & \\ \cmidrule(lr){2-4}
  & Full Constructor & 58 & 0.02\% & & \\ \cmidrule(lr){2-4}
  & Full Class & 37 & 0.01\% & & \\ \cmidrule(lr){2-4}
  & Full Enum & 24 & 0.01\% & & \\ \bottomrule
\end{tabular}
\caption{Number of clone instances for clone contents categories}
\label{tab:contents}
\end{table}

@@

\begin{table}[H]
\centering
\begin{tabular}{@{}lrrrrr@{}}
\toprule
                         & \makecell{# clones\\(Fontana et al.)} & \makecell{Percentage\\(Fontana et al.)} & \makecell{Percentage\\(Our Work)} \\ \midrule
Same Class               & 5,645  & 32.1\%     & 26.8\%    \\
Same External Superclass & 4,384  & 25.0\%     & 20.6\%   \\
Unrelated Class          & 2,758  & 15.7\%     & 18.4\%    \\
Sibling Class            & 2,721  & 15.5\%     & 18.2\%    \\
Common Hierarchy Class   & 970    & 5.5\%      & 0.8\%    \\
Same Method              & 569    & 3.2\%      & 10.5\%    \\
First Cousin Class       & 416    & 2.4\%      & 1.4\%    \\
Superclass               & 91     & 0.5\%      & 3.1\%    \\
Ancestor Class           & 13     & 0.1\%      & 0.2\%    \\ \bottomrule
\end{tabular}
\caption{Clone relation analysis by Fontana et al. \cite{fontana2012duplicated} measured over the Qualitas Corpus \cite{tempero2010qualitas}.}
\label{tab:dcra-relation}
\end{table}

>>>>

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage{float}
\usepackage{hyperref}
\usepackage[style=ieee,citestyle=numeric-comp,dashed=false]{biblatex}
\usepackage{booktabs}
\usepackage{multirow}
\addbibresource{refs.bib}
\usepackage{makecell}

@@

\begin{table}[H]
\centering
\caption{Number of clone classes per clone relation.}
\begin{tabular}{@{}l|l|rr|rr@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{Relation}} & \textit{\textbf{Clone Classes}} & \textit{\textbf{\%}} & \textit{\textbf{Total}} & \textit{\textbf{\%}} \\ \midrule
\multirow{2}{*}{Common Class} & Same Class & 22,893 & 26.8\% & \multirow{2}{*}{31,848} & \multirow{2}{*}{37.2\%} \\ \cmidrule(lr){2-4}
 & Same Method & 8,955 & 10.5\% & & \\ \midrule
\multirow{5}{*}{Common Hierarchy} & Sibling & 15,588 & 18.2\% & \multirow{5}{*}{20,342}& \multirow{5}{*}{23.8\%} \\ \cmidrule(lr){2-4}
 & Superclass & 2,616 & 3.1\% & & \\ \cmidrule(lr){2-4}
 & First Cousin & 1,219 & 1.4\% & & \\ \cmidrule(lr){2-4}
 & Common Hierarchy & 720 & 0.8\% & & \\ \cmidrule(lr){2-4}
 & Ancestor & 199 & 0.2\% & & \\ \midrule
\multirow{4}{*}{Unrelated} & No Direct Superclass & 10,677 & 12.5\% & \multirow{4}{*}{20,314}& \multirow{4}{*}{23.7\%} \\ \cmidrule(lr){2-4}
 & External Superclass & 4,525 & 5.3\% & & \\ \cmidrule(lr){2-4}
 & External Ancestor & 3,347 & 3.9\% & & \\ \cmidrule(lr){2-4}
 & No Indirect Superclass & 1,765 & 2.1\% & & \\ \midrule
\multirow{2}{*}{Common Interface} & Same Direct Interface & 7,522 & 8.8\% & \multirow{2}{*}{13,074} & \multirow{2}{*}{15.3\%} \\ \cmidrule(lr){2-4}
 & Same Indirect Interface & 5,552 & 6.5\% & & \\ \bottomrule
\end{tabular}
\label{tab:relation}
\end{table}

@@

\begin{table}[H]
\centering
\caption{Amount of clone instances with a per location category.}
\begin{tabular}{@{}lrr@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{Clone instances}} & \textit{\textbf{\%}} \\ \midrule
Method Level & 232,545 & 78.43\% \\
Class Level & 50,402 & 17.00\% \\
Constructor Level & 10,039 & 3.39\% \\
Interface Level & 2,693 & 0.91\% \\
Enum Level & 788 & 0.27\% \\
\end{tabular}
\label{tab:location}
\end{table}

@@

\begin{table}[H]
\centering
\caption{Number of clone instances for clone contents categories}
\begin{tabular}{@{}l|l|rr|rr@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{Contents}} & \textit{\textbf{Clone instances}} & \textit{\textbf{\%}} & \textit{\textbf{Total}} & \textit{\textbf{\%}} \\ \midrule
\multirow{2}{*}{Partial} & Method Body & 219,540 & 74.05\% & \multirow{2}{*}{229,521}& \multirow{2}{*}{77.42\%} \\ \cmidrule(lr){2-4}
 & Constructor Body & 9,981 & 3.37\% & & \\ \midrule
\multirow{3}{*}{Other} & Several Methods & 22,749 & 7.67\% & \multirow{3}{*}{53,773} & \multirow{3}{*}{18.14\%} \\ \cmidrule(lr){2-4}
 & Only Fields & 17,700 & 5.97\% & & \\ \cmidrule(lr){2-4}
 & Other & 13,324 & 4.49\% & & \\ \midrule
 \multirow{5}{*}{Full} & Full Method & 12,990 & 4.38\% & \multirow{5}{*}{13,173}& \multirow{5}{*}{4,44\%} \\ \cmidrule(lr){2-4}
  & Full Interface & 64 & 0.02\% & & \\ \cmidrule(lr){2-4}
  & Full Constructor & 58 & 0.02\% & & \\ \cmidrule(lr){2-4}
  & Full Class & 37 & 0.01\% & & \\ \cmidrule(lr){2-4}
  & Full Enum & 24 & 0.01\% & & \\ \bottomrule
\end{tabular}
\label{tab:contents}
\end{table}

@@

\begin{table}[H]
\centering
\caption{Clone relation analysis by Fontana et al. \cite{fontana2012duplicated} measured over the Qualitas Corpus \cite{tempero2010qualitas}.}
\begin{tabular}{@{}lrrrrr@{}}
\toprule
                         & \makecell{Nr. of clones\\(Fontana et al.)} & \makecell{Percentage\\(Fontana et al.)} & \makecell{Percentage\\(Our Work)} \\ \midrule
Same Class               & 5,645  & 32.1\%     & 26.8\%    \\
Same External Superclass & 4,384  & 25.0\%     & 20.6\%   \\
Unrelated Class          & 2,758  & 15.7\%     & 18.4\%    \\
Sibling Class            & 2,721  & 15.5\%     & 18.2\%    \\
Common Hierarchy Class   & 970    & 5.5\%      & 0.8\%    \\
Same Method              & 569    & 3.2\%      & 10.5\%    \\
First Cousin Class       & 416    & 2.4\%      & 1.4\%    \\
Superclass               & 91     & 0.5\%      & 3.1\%    \\
Ancestor Class           & 13     & 0.1\%      & 0.2\%    \\ \bottomrule
\end{tabular}

\label{tab:dcra-relation}
\end{table}
